---
title: "Germany data on district level"
output: 
  github_document:
  html_document:
    toc: true
    dev: svg
---

> COVID-19 District level data from Robert Koch Institute in Germany

To retrieve the lastest yourself use the `rki.de.district.data::update.dataset()` function inside the R package. Note that, as of now, the data is updated by the Robert Koch Institute once a day.

It is downloaded from ARCGIS REST API using the [RKI_COVID19](https://services7.arcgis.com/mOBPykOjAyBO2ZKk/arcgis/rest/services/RKI_COVID19/FeatureServer/0/query?where=Meldedatum+%3E+(CURRENT_TIMESTAMP+-+3)&objectIds=&time=&resultType=none&outFields=*&returnIdsOnly=false&returnUniqueIdsOnly=false&returnCountOnly=false&returnDistinctValues=false&cacheHint=false&orderByFields=Meldedatum&outStatistics=&having=&resultOffset=&resultRecordCount=&sqlFormat=none&f=html&token=) feature server.

## Install / Usage

The data is available inside the `data/` folder in `.csv` format. 

It can also be used as an R package by installing this repository directly:

```{r, eval=FALSE, echo = TRUE}
> BiocManager::install_github('averissimo/covid19-de_rki-data')`
> `devtools::install_github('averissimo/covid19-de_rki-data')`
```

```{r, eval=FALSE, include=FALSE}
rmarkdown::render('download.Rmd', output_format = rmarkdown::github_document(), output_file = 'README.md')
unlink('../README.md')
unlink('../README_files', recursive = TRUE, force = TRUE)
file.copy('README.md', '../README.md')
file.copy('README_files', '..', recursive = TRUE, overwrite = TRUE)
unlink('README.md')
unlink('README.html')
unlink('README_files', recursive = TRUE, force = TRUE)
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, collapse = TRUE)
library(tidyverse)
library(rjson)
library(anytime)
library(glue)
library(DT)
library(futile.logger)
library(viridis)
library(ggthemes)
library(ggrepel)

flog.threshold('info')
flog.layout(layout.format('~m'))

Sys.setlocale('LC_TIME', 'en_GB.UTF-8')

devtools::load_all()
```

## Update data in package

```{r, echo=TRUE}
rki.covid19.tmp <- update.dataset()
```

```{r, include=FALSE}
data('rki.covid19')
if (!exists('rki.covid19') || (!all(rki.covid19.tmp$object.id %in% rki.covid19$object.id))) {
  rki.covid19 <- rki.covid19.tmp
  usethis::use_data(rki.covid19, overwrite = TRUE)
  write_csv2(rki.covid19, path = '../data/rki.covid19.csv')
}
```


```{r, include=FALSE}
my.rki <- rki.covid19 %>%
  add.factors %>% 
  #group_by(id.state, state, id.district, district, gender, age.group) %>%
  arrange(date)

top.states <- my.rki %>% group_by(state) %>% summarise(cases = sum(deaths) * sum(cases)) %>% arrange(-cases) %>% pull(state)
top.districts <- my.rki %>% group_by(district) %>% summarise(cases = sum(deaths) * sum(cases)) %>% arrange(-cases) %>% pull(district)
```

## New cases/deaths per day in most affected states/districts {.tabset .tabset-fade .tabset-pills}

### New Cases in states

```{r}
my.rki %>% 
  filter(state %in% (top.states %>% head(6))) %>%
  filter(anydate(base::date()) - date <= 12) %>% 
  arrange(desc(date)) %>% 
  group_by(state, date) %>%
  summarize(cases = sum(cases)) %>%
  arrange(date) %>% 
  mutate(label = if_else(date == last(date), paste0(state, ' (', format(cases, big.mark = ','), ')'),'')) %>% 
  ggplot(aes(x = date, y = cases, color = state)) + 
    geom_line(size = 1.2) + 
    geom_point(size = 2) + 
    geom_label_repel(aes(label = label, fill = state), 
                     na.rm = TRUE, alpha = .8, color = 'white', size = 3, segment.alpha = .4, segment.colour = 'black', force = 5) +
    scale_color_viridis_d(end = .8) + 
    scale_fill_viridis_d(end = .8) + 
    theme_minimal() +
    theme(legend.position = 'none') +
    labs(title = 'New cases per day in last 12 days', y = 'Cases', x = 'Day')
```

### New Deaths in states

```{r}
my.rki %>% 
  filter(state %in% (top.states %>% head(6))) %>%
  filter(anydate(base::date()) - date <= 12) %>% 
  arrange(desc(date)) %>% 
  group_by(state, date) %>%
  summarize(cases = sum(deaths)) %>%
  arrange(date) %>% 
  mutate(label = if_else(date == last(date), paste0(state, ' (', format(cases, big.mark = ','), ')'),'')) %>% 
  ggplot(aes(x = date, y = cases, color = state)) + 
    geom_line(size = 1.2) + 
    geom_point(size = 2) + 
    geom_label_repel(aes(label = label, fill = state), 
                     na.rm = TRUE, alpha = .8, color = 'white', size = 3, segment.alpha = .4, segment.colour = 'black', force = 5) +
    scale_color_viridis_d(end = .8) + 
    scale_fill_viridis_d(end = .8) + 
    theme_minimal() +
    theme(legend.position = 'none') +
    labs(title = 'New deaths per day in last 12 days', y = 'Deaths', x = 'Day')
```

### New cases in districts

```{r}
my.rki %>% 
  filter(district %in% (top.districts %>% head(5))) %>%
  filter(anydate(base::date()) - date <= 12) %>% 
  arrange(desc(date)) %>% 
  group_by(district, date) %>%
  summarize(cases = sum(cases)) %>%
  arrange(date) %>% 
  mutate(label = if_else(date == last(date), paste0(district, ' (', format(cases, big.mark = ','), ')'),'')) %>% 
  ggplot(aes(x = date, y = cases, color = district)) + 
    geom_line(size = 1.2) + 
    geom_point(size = 2) + 
    geom_label_repel(aes(label = label, fill = district), 
                     na.rm = TRUE, alpha = .8, color = 'white', size = 3, segment.alpha = .4, segment.colour = 'black', force = 4) +
    scale_color_viridis_d(end = .9) + 
    scale_fill_viridis_d(end = .9) + 
    theme_minimal() +
    theme(legend.position = 'none') +
    labs(title = 'New cases per day in last 12 days', y = 'Cases', x = 'Day')
```

### New deaths in districts

```{r}
my.rki %>% 
  filter(district %in% (top.districts %>% head(5))) %>%
  filter(anydate(base::date()) - date <= 12) %>% 
  arrange(desc(date)) %>% 
  group_by(district, date) %>%
  summarize(cases = sum(deaths)) %>%
  arrange(date) %>% 
  mutate(label = if_else(date == last(date), paste0(district, ' (', format(cases, big.mark = ','), ')'),'')) %>% 
  ggplot(aes(x = date, y = cases, color = district)) + 
    geom_line(size = 1.2) + 
    geom_point(size = 2) + 
    geom_label_repel(aes(label = label, fill = district), 
                     na.rm = TRUE, alpha = .8, color = 'white', size = 3, segment.alpha = .4, segment.colour = 'black', force = 4) +
    scale_color_viridis_d(end = .9) + 
    scale_fill_viridis_d(end = .9) + 
    theme_minimal() +
    theme(legend.position = 'none') +
    labs(title = 'New cases per day in last 12 days', y = 'Cases', x = 'Day')
```

## Total cases in last 12 days in most affected states/districts {.tabset .tabset-fade .tabset-pills}

### Total cases in states

Showing only 6 states most affected

```{r}
my.rki %>% 
  filter(state %in% (top.states %>% head(6))) %>%
  filter(anydate(base::date()) - date <= 12) %>% 
  arrange(date) %>% 
  group_by(state, date) %>%
  summarize(cases = sum(cases)) %>%
  mutate(cumul.cases = cumsum(cases),
         label = if_else(date == last(date), paste0(state, '(', format(cumul.cases, big.mark=','), ')'), '')) %>%
  ggplot(aes(x = date, y = cumul.cases, color = state)) + 
    geom_line(size = 1.2) + 
    geom_point(size = 2) + 
    geom_label_repel(aes(label = label, fill = state), 
                     na.rm = TRUE, alpha = .8, color = 'white', size = 3, segment.alpha = .4, segment.colour = 'black', force = 2) +
    scale_color_viridis(discrete = TRUE, end = .5) +
    scale_fill_viridis(discrete = TRUE, end = .5) + 
    theme_minimal() +
    theme(legend.position = 'none')
```

### Total deaths in states

Showing only 6 states most affected

```{r}
my.rki %>% 
  filter(state %in% (top.states %>% head(6))) %>%
  filter(anydate(base::date()) - date <= 12) %>% 
  arrange(date) %>% 
  group_by(state, date) %>%
  summarize(cases = sum(deaths)) %>%
  mutate(cumul.cases = cumsum(cases),
         label = if_else(date == last(date), paste0(state, '(', format(cumul.cases, big.mark=','), ')'), '')) %>%
  ggplot(aes(x = date, y = cumul.cases, color = state)) + 
    geom_line(size = 1.2) + 
    geom_point(size = 2) + 
    geom_label_repel(aes(label = label, fill = state), 
                     na.rm = TRUE, alpha = .8, color = 'white', size = 3, segment.alpha = .4, segment.colour = 'black', force = 2) +
    scale_color_viridis(discrete = TRUE, end = .5) +
    scale_fill_viridis(discrete = TRUE, end = .5) + 
    theme_minimal() +
    theme(legend.position = 'none')
```

### Total cases in districs

Showing only 6 districs most affected

```{r}
my.rki %>% 
  filter(district %in% (top.districts %>% head(6))) %>%
  filter(anydate(base::date()) - date <= 12) %>% 
  arrange(date) %>% 
  group_by(district, date) %>%
  summarize(cases = sum(cases)) %>%
  mutate(cumul.cases = cumsum(cases),
         label = if_else(date == last(date), paste0(district, '(', format(cumul.cases, big.mark=','), ')'), '')) %>%
  ggplot(aes(x = date, y = cumul.cases, color = district)) + 
    geom_line(size = 1.2) + 
    geom_point(size = 2) + 
    geom_label_repel(aes(label = label, fill = district), 
                     na.rm = TRUE, alpha = .8, color = 'white', size = 3, segment.alpha = .4, segment.colour = 'black', force = 2) +
    scale_color_viridis(discrete = TRUE, end = .5) +
    scale_fill_viridis(discrete = TRUE, end = .5) + 
    theme_minimal() +
    theme(legend.position = 'none')
```

### Total deaths in districs

Showing only 6 districs most affected

```{r}
my.rki %>% 
  filter(district %in% (top.districts %>% head(6))) %>%
  filter(anydate(base::date()) - date <= 12) %>% 
  arrange(date) %>% 
  group_by(district, date) %>%
  summarize(cases = sum(deaths)) %>%
  mutate(cumul.cases = cumsum(cases),
         label = if_else(date == last(date), paste0(district, '(', format(cumul.cases, big.mark=','), ')'), '')) %>%
  ggplot(aes(x = date, y = cumul.cases, color = district)) + 
    geom_line(size = 1.2) + 
    geom_point(size = 2) + 
    geom_label_repel(aes(label = label, fill = district), 
                     na.rm = TRUE, alpha = .8, color = 'white', size = 3, segment.alpha = .4, segment.colour = 'black', force = 2) +
    scale_color_viridis(discrete = TRUE, end = .5) +
    scale_fill_viridis(discrete = TRUE, end = .5) + 
    theme_minimal() +
    theme(legend.position = 'none')
```

## Cases by age groups {.tabset .tabset-fade .tabset-pills}

### Cases in states

```{r}
age.plot.state(my.rki, 'cases', top.states %>% head(6), 'Number of Cases')
```

### Deaths in states

```{r}
age.plot.state(my.rki, 'deaths', top.states %>% head(6), 'Number of Deaths')
```

### Cases in districts

```{r}
age.plot.district(my.rki, 'cases', top.districts %>% head(6), 'Number of Cases')
```

### Deaths in districts

```{r}
age.plot.district(my.rki, 'deaths', top.districts %>% head(6), 'Number of Deaths')
```



