---
title: "Germany data on district level"
output: 
  html_document:
    toc: true
    dev: svg
    self_contained: false
  github_document:
    dev: svg
---

```{r, eval=FALSE, include=FALSE}
rmarkdown::render('_README.Rmd', output_format = 'github_document', output_file = 'README.md')
if (file.exists(file.path('README.html')) { unlink('README.html') }
if (file.exists(file.path('..', 'README.md')) { unlink('../README.md') }
if (dir.exists(file.path('..', 'README_files')) { unlink('../README.md', recursive = TRUE, force = TRUE) }
file.rename('README.md', '../README.md')
file.rename('README_files', '../README_files')
rmarkdown::render_site(output_format = 'html_document')
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, collapse = TRUE, fig.height=8, fig.width=10)
library(tidyverse)
library(rjson)
library(glue)
library(DT)
library(anytime)
library(futile.logger)
library(httr)
library(ggrepel)
library(ggthemes)
library(viridis)
library(reshape2)

flog.threshold('info')
flog.layout(layout.format('~m'))

Sys.setlocale('LC_TIME', 'en_GB.UTF-8')

devtools::load_all()
```

> COVID-19 District level data from Robert Koch Institute in Germany

The data is updated daily and is downloaded from a ARCGIS REST API using the [RKI_COVID19](https://services7.arcgis.com/mOBPykOjAyBO2ZKk/arcgis/rest/services/RKI_COVID19/FeatureServer/0/query?where=Meldedatum+%3E+(CURRENT_TIMESTAMP+-+3)&objectIds=&time=&resultType=none&outFields=*&returnIdsOnly=false&returnUniqueIdsOnly=false&returnCountOnly=false&returnDistinctValues=false&cacheHint=false&orderByFields=Meldedatum&outStatistics=&having=&resultOffset=&resultRecordCount=&sqlFormat=none&f=html&token=) feature server.

Data from previous dates can be changed over time and update the data files accordingly, therefore `object.id` for any given row will change daily.

Source code available at [averissimo/covid19-rki_de-data](https://github.com/averissimo/covid19.de.data).

**Other covid-19 confirmed/deaths analysis**

* [World](https://averissimo.github.io/covid19-analysis/)
* [Germany](https://averissimo.github.io/covid19-analysis/germany.html) *(by state)*
* [Italy](https://averissimo.github.io/covid19-analysis/italy.html) *(by region)*
* [Spain](https://averissimo.github.io/covid19-analysis/spain.html) *(by region)*

**Age group analysis**

* [Germany](https://averissimo.github.io/covid19.de.data/) *(by state and district)*


## Install / Usage

The data is available inside the `data/` folder in `.csv` format. 

It can also be used as an *R package* by installing this repository directly:

```{r, eval=FALSE, echo=TRUE}
BiocManager::install_github('averissimo/covid19.de.data')
# or
devtools::install_github('averissimo/covid19.de.data')
```

## Update data

To retrieve the lastest yourself use the following function of the R package. 

```{r, eval=FALSE, echo=TRUE}
covid19.de.data::update_dataset()
covid19.de.data::update_dataset.no.age()
```

Note that, as of now, the data is updated by the Robert Koch Institute once a day.

```{r update_datasetss, include=FALSE}
rki.covid19.tmp <- update_dataset()
rki.covid19.tmp2 <- update_dataset.no.age(force.all = TRUE)
```

```{r, include=FALSE}
data('rki.covid19.no.age')
if (!exists('rki.covid19.no.age') || (!all(rki.covid19.tmp2$object.id %in% rki.covid19.no.age$object.id))) {
  rki.covid19.no.age <- rki.covid19.tmp2
  usethis::use_data(rki.covid19.no.age, overwrite = TRUE)
  write_csv2(rki.covid19.no.age, path = '../data/rki.covid19_no_age.csv')
}
```

```{r, include=FALSE}
data('rki.covid19')
if (!exists('rki.covid19') || (!all(rki.covid19.tmp$object.id %in% rki.covid19$object.id))) {
  rki.covid19 <- rki.covid19.tmp
  usethis::use_data(rki.covid19, overwrite = TRUE)
  write_csv2(rki.covid19, path = '../data/rki.covid19.csv')
}
```


```{r, include=FALSE}
my.rki <- rki.covid19 %>%
  group_by(date, id.state, state, NUTS_3, NUTS_3.code, age.group, gender) %>% 
  summarise(cases = sum(cases) ,deaths = sum(deaths)) %>% 
  ungroup() %>% 
  select(date, id.state, state, district = NUTS_3, id.district = NUTS_3.code, age.group, gender, cases, deaths) %>% 
  add.factors %>% 
  #group_by(id.state, state, id.district, district, gender, age.group) %>%
  arrange(date)

top.states <- my.rki %>% group_by(state) %>% summarise(cases = sum(cases)) %>% arrange(-cases) %>% pull(state)
top.districts <- my.rki %>% group_by(district) %>% summarise(cases = sum(cases)) %>% arrange(-cases) %>% pull(district)

last.date.string <- 'Latest data from {my.rki %>% pull(date) %>% max}' %>% glue
```

## Data visualization

### Cases by age groups in Germany {.tabset .tabset-fade .tabset-pills}

#### Cases in Germany

```{r, fig.width=4.5, fig.height=4}
my.rki %>% 
  mutate(state = 'Germany') %>% 
  select(-district, -id.district, -id.state, -date) %>% 
  group_by(state, age.group, gender) %>% 
  summarise(cases = sum(cases), deaths = sum(deaths)) %>% 
age.plot.state('cases', c(), 'Cases in Germany', FALSE, '')
```
```{r, fig.width=4.5, fig.height=4}
my.rki %>% 
  mutate(state = 'Germany') %>% 
  select(-district, -id.district, -id.state, -date) %>% 
  group_by(state, age.group, gender) %>% 
  summarise(cases = sum(cases), deaths = sum(deaths)) %>% 
age.plot.state('deaths', c(), 'Deaths in Germany', FALSE, '')
```

### Cases by day {.tabset .tabset-fade .tabset-pills}

```{r, results='asis', fig.width=4.5, fig.height=4}
age.by.day <- my.rki %>% 
  mutate(state = 'Germany') %>% 
  select(-district, -id.district, -id.state) %>% 
  group_by(state, age.group, gender, date) %>% 
  filter(gender != 'unbekannt') %>% 
  summarise(cases = sum(cases), deaths = sum(deaths)) %>% 
  mutate(cases = if_else(gender == 'M', cases * -1, cases),
         deaths = if_else(gender == 'M', deaths * -1, deaths))

age.ix <- age.by.day$date %>% unique %>% sort(decreasing = TRUE)

confirmed.max <- age.by.day %>% pull(cases) %>% max
death.max <- age.by.day %>% pull(deaths) %>% max

for (ix.aux in seq_along(age.ix)) {
  ix <- age.ix[ix.aux]
  cat('\n')
  cat('\n')
  
  cat('#### {ix}' %>% glue)
  
  cat('\n')
  cat('\n')
  cat('\n')
  
  print(
    age.by.day %>% 
      filter(date == ix) %>%
      ggplot(aes(x = cases, y = age.group, fill = gender)) +
      geom_bar(stat = 'identity') + 
      expand_limits(x =c(-1 * confirmed.max, confirmed.max)) +
      scale_x_continuous('', labels = function(ix) { return(abs(ix)) }) +
      scale_y_discrete(limits = age.by.day$age.group %>% unique %>% sort) + 
      scale_fill_viridis_d(end = .8) + 
      labs(title = "Confirmed cases from {ix}" %>% glue,
           y = 'Age group',
           x = 'Confirmed Cases') +
      theme_minimal() + 
      theme(legend.position = 'bottom')
  )
  
  print(
    age.by.day %>% 
      filter(date == ix) %>%
      ggplot(aes(x = deaths, y = age.group, fill = gender)) +
      geom_bar(stat = 'identity') + 
      expand_limits(x =c(-1 * death.max, death.max)) +
      scale_x_continuous('', labels = function(ix) { return(abs(ix)) }) +
      scale_y_discrete(limits = age.by.day$age.group %>% unique %>% sort) + 
      scale_fill_viridis_d(end = .8) + 
      labs(title = "Deaths from {ix}" %>% glue,
           y = 'Age group',
           x = 'Deaths') +
      theme_minimal() + 
      theme(legend.position = 'bottom')
  )
    
  cat('\n')
  cat('\n')
}
```

### Cases by age groups {.tabset .tabset-fade .tabset-pills}

#### Cases in states

```{r age.state.cases}
age.plot.state(my.rki, 'cases', top.states %>% head(8), 'Cases in States')
```

#### Deaths in states

```{r age.state.deaths}
age.plot.state(my.rki, 'deaths', top.states %>% head(8), 'Deaths in States')
```

#### Cases in districts

```{r age.district.cases}
age.plot.district(my.rki, 'cases', top.districts %>% head(8), 'Number of Cases')
```

#### Deaths in districts

```{r age.district.}
age.plot.district(my.rki, 'deaths', top.districts %>% head(8), 'Number of Deaths')
```

### Cases by Federal State {.tabset .tabset-fade .tabset-pills}

#### Confirmed cases

```{r bar_plot_cases_state}
sum.rki <- my.rki %>% 
  group_by(state) %>% 
  summarise(cases = sum(cases), deaths = sum(deaths)) %>% 
  melt(id.vars = 'state', variable.name = 'type', value.name = 'cases') %>% 
  mutate(type = if_else(type == 'cases', 'confirmed', 'death'))
top30(sum.rki, 'confirmed', 'Federal State')
```

#### Deaths

```{r bar_plot_deaths_state}
top30(sum.rki, 'death', 'Federal State')
```

### Cases by Districts *(Showing only 50 districts with most cases/deaths)* {.tabset .tabset-fade .tabset-pills}

#### Confirmed cases

*Showing only 50*

```{r bar_plot_cases_district}
sum.rki.dist <- my.rki %>% 
  group_by(district) %>% 
  summarise(cases = sum(cases), deaths = sum(deaths)) %>% 
  melt(id.vars = 'district', variable.name = 'type', value.name = 'cases') %>% 
  mutate(type = if_else(type == 'cases', 'confirmed', 'death')) %>% 
  select(state = district, type, cases)
  
top30(sum.rki.dist, 'confirmed', 'District', 50)
```

#### Deaths

*Showing only 50*

```{r bar_plot_death_district}
top30(sum.rki.dist, 'death', 'District', 50)
```


### New cases/deaths per day *in most affected states/districts* {.tabset .tabset-fade .tabset-pills}

#### New Cases in states

```{r new_cases_states}
my.rki %>% 
  filter(state %in% (top.states %>% head(8))) %>%
  filter(anydate(base::date()) - date <= 12) %>% 
  arrange(desc(date)) %>% 
  group_by(state, date) %>%
  summarize(cases = sum(cases)) %>%
  arrange(date) %>% 
  mutate(label = if_else(date == last(date), paste0(state, ' (', format(cases, big.mark = ','), ')'),'')) %>% 
  ggplot(aes(x = date, y = cases, color = state)) + 
    geom_line(size = 1.2) + 
    geom_point(size = 2) + 
    geom_label_repel(aes(label = label, fill = state), 
                     na.rm = TRUE, alpha = .8, color = 'white', size = 3, segment.alpha = .4, segment.colour = 'black', force = 5) +
    scale_color_viridis_d(end = .8) + 
    scale_fill_viridis_d(end = .8) + 
    theme_minimal() +
    theme(legend.position = 'none') +
    labs(title = 'New cases per day in last 12 days', y = 'Cases', x = 'Day',
         subtitle = 'Showing only 8 most affected states')
```

#### New Deaths in states

```{r new_deaths_states}
my.rki %>% 
  filter(state %in% (top.states %>% head(8))) %>%
  filter(anydate(base::date()) - date <= 12) %>% 
  arrange(desc(date)) %>% 
  group_by(state, date) %>%
  summarize(cases = sum(deaths)) %>%
  arrange(date) %>% 
  mutate(label = if_else(date == last(date), paste0(state, ' (', format(cases, big.mark = ','), ')'),'')) %>% 
  ggplot(aes(x = date, y = cases, color = state)) + 
    geom_line(size = 1.2) + 
    geom_point(size = 2) + 
    geom_label_repel(aes(label = label, fill = state), 
                     na.rm = TRUE, alpha = .8, color = 'white', size = 3, segment.alpha = .4, segment.colour = 'black', force = 5) +
    scale_color_viridis_d(end = .8) + 
    scale_fill_viridis_d(end = .8) + 
    theme_minimal() +
    theme(legend.position = 'none') +
    labs(title = 'New deaths per day in last 12 days', y = 'Deaths', x = 'Day',
         subtitle = 'Showing only 8 most affected states')
```

#### New cases in districts

```{r new_cases_districts}
my.rki %>% 
  filter(district %in% (top.districts %>% head(8))) %>%
  filter(anydate(base::date()) - date <= 12) %>% 
  arrange(desc(date)) %>% 
  group_by(district, date) %>%
  summarize(cases = sum(cases)) %>%
  arrange(date) %>% 
  mutate(label = if_else(date == last(date), paste0(district, ' (', format(cases, big.mark = ','), ')'),'')) %>% 
  ggplot(aes(x = date, y = cases, color = district)) + 
    geom_line(size = 1.2) + 
    geom_point(size = 2) + 
    geom_label_repel(aes(label = label, fill = district), 
                     na.rm = TRUE, alpha = .8, color = 'white', size = 3, segment.alpha = .4, segment.colour = 'black', force = 4) +
    scale_color_viridis_d(end = .9) + 
    scale_fill_viridis_d(end = .9) + 
    theme_minimal() +
    theme(legend.position = 'none') +
    labs(title = 'New cases per day in last 12 days', y = 'Cases', x = 'Day',
         subtitle = 'Showing only 8 most affected states')
```

#### New deaths in districts

```{r new_deaths_districts}
my.rki %>% 
  filter(district %in% (top.districts %>% head(8))) %>%
  filter(anydate(base::date()) - date <= 12) %>% 
  arrange(desc(date)) %>% 
  group_by(district, date) %>%
  summarize(cases = sum(deaths)) %>%
  arrange(date) %>% 
  mutate(label = if_else(date == last(date), paste0(district, ' (', format(cases, big.mark = ','), ')'),'')) %>% 
  ggplot(aes(x = date, y = cases, color = district)) + 
    geom_line(size = 1.2) + 
    geom_point(size = 2) + 
    geom_label_repel(aes(label = label, fill = district), 
                     na.rm = TRUE, alpha = .8, color = 'white', size = 3, segment.alpha = .4, segment.colour = 'black', force = 4) +
    scale_color_viridis_d(end = .9) + 
    scale_fill_viridis_d(end = .9) + 
    theme_minimal() +
    theme(legend.position = 'none') +
    labs(title = 'New cases per day in last 12 days', y = 'Cases', x = 'Day',
         subtitle = 'Showing only 8 most affected districts')
```

### Total cases in last 12 days *in most affected states/districts* {.tabset .tabset-fade .tabset-pills}

#### Total cases in states

```{r total_cases_states}
my.rki %>% 
  filter(state %in% (top.states %>% head(8))) %>%
  filter(anydate(base::date()) - date <= 12) %>% 
  arrange(date) %>% 
  group_by(state, date) %>%
  summarize(cases = sum(cases)) %>%
  mutate(cumul.cases = cumsum(cases),
         label = if_else(date == last(date), paste0(state, '(', format(cumul.cases, big.mark=','), ')'), '')) %>%
  ggplot(aes(x = date, y = cumul.cases, color = state)) + 
    geom_line(size = 1.2) + 
    geom_point(size = 2) + 
    geom_label_repel(aes(label = label, fill = state), 
                     na.rm = TRUE, alpha = .8, color = 'white', size = 3, segment.alpha = .4, segment.colour = 'black', force = 2) +
    scale_color_viridis(discrete = TRUE, end = .5) +
    scale_fill_viridis(discrete = TRUE, end = .5) + 
    theme_minimal() +
    theme(legend.position = 'none') +
    labs(title = 'Total cases per day in last 12 days', y = 'Total Cases', x = 'Day',
         subtitle = 'Showing only 8 most affected states')
```

#### Total deaths in states

Showing only 6 states most affected

```{r total_deaths_states}
my.rki %>% 
  filter(state %in% (top.states %>% head(8))) %>%
  filter(anydate(base::date()) - date <= 12) %>% 
  arrange(date) %>% 
  group_by(state, date) %>%
  summarize(cases = sum(deaths)) %>%
  mutate(cumul.cases = cumsum(cases),
         label = if_else(date == last(date), paste0(state, '(', format(cumul.cases, big.mark=','), ')'), '')) %>%
  ggplot(aes(x = date, y = cumul.cases, color = state)) + 
    geom_line(size = 1.2) + 
    geom_point(size = 2) + 
    geom_label_repel(aes(label = label, fill = state), 
                     na.rm = TRUE, alpha = .8, color = 'white', size = 3, segment.alpha = .4, segment.colour = 'black', force = 2) +
    scale_color_viridis(discrete = TRUE, end = .5) +
    scale_fill_viridis(discrete = TRUE, end = .5) + 
    theme_minimal() +
    theme(legend.position = 'none') +
    labs(title = 'Total deaths per day in last 12 days', y = 'Total Deaths', x = 'Day',
         subtitle = 'Showing only 8 most affected states')
```

#### Total cases in districs

Showing only 6 districs most affected

```{r total_cases_districts}
my.rki %>% 
  filter(district %in% (top.districts %>% head(8))) %>%
  filter(anydate(base::date()) - date <= 12) %>% 
  arrange(date) %>% 
  group_by(district, date) %>%
  summarize(cases = sum(cases)) %>%
  mutate(cumul.cases = cumsum(cases),
         label = if_else(date == last(date), paste0(district, '(', format(cumul.cases, big.mark=','), ')'), '')) %>%
  ggplot(aes(x = date, y = cumul.cases, color = district)) + 
    geom_line(size = 1.2) + 
    geom_point(size = 2) + 
    geom_label_repel(aes(label = label, fill = district), 
                     na.rm = TRUE, alpha = .8, color = 'white', size = 3, segment.alpha = .4, segment.colour = 'black', force = 2) +
    scale_color_viridis(discrete = TRUE, end = .5) +
    scale_fill_viridis(discrete = TRUE, end = .5) + 
    theme_minimal() +
    theme(legend.position = 'none') +
    labs(title = 'Total cases per day in last 12 days', y = 'Total Cases', x = 'Day',
         subtitle = 'Showing only 8 most affected districts')
```

#### Total deaths in districs

Showing only 6 districs most affected

```{r total_deaths_districts}
my.rki %>% 
  filter(district %in% (top.districts %>% head(8))) %>%
  filter(anydate(base::date()) - date <= 12) %>% 
  arrange(date) %>% 
  group_by(district, date) %>%
  summarize(cases = sum(deaths)) %>%
  mutate(cumul.cases = cumsum(cases),
         label = if_else(date == last(date), paste0(district, '(', format(cumul.cases, big.mark=','), ')'), '')) %>%
  ggplot(aes(x = date, y = cumul.cases, color = district)) + 
    geom_line(size = 1.2) + 
    geom_point(size = 2) + 
    geom_label_repel(aes(label = label, fill = district), 
                     na.rm = TRUE, alpha = .8, color = 'white', size = 3, segment.alpha = .4, segment.colour = 'black', force = 2) +
    scale_color_viridis(discrete = TRUE, end = .5) +
    scale_fill_viridis(discrete = TRUE, end = .5) + 
    theme_minimal() +
    theme(legend.position = 'none') +
    labs(title = 'Total deaths per day in last 12 days', y = 'Total Deaths', x = 'Day',
         subtitle = 'Showing only 8 most affected districts')
```


